\PYGEOMETRY{}: a Python library for the creation of Monte Carlo radiation transport physical geometries

### 2020-09-14 public/paper/pyg4ometry.tex
combine the two adjacent references to the same Listing
looks awkward when we say "Listing 2" twice right next to each other.
remove and/or, replace with or

\section{Rapid geometry modelling}
Given the Python scripting interface, expression  and tessellation engines it is possible for a user to rapidly specify the geometrical layout of the RT problem, vary 
the parameters of the geometry and visualise it.  When a user has achieved the desired geometry, without geometry overlaps, a GDML file can be written to disk from the internal memory representation. Some example code is presented in Listing~\ref{lst:pythonRapidModelling}. The structure should be familiar to regular 
users of Geant4 or GDML, apart from the new class described in the previous section called the \pyinline{Registry}. First the \verb|Registry| is created to store all the \PYGEOMETRY{} objects; followed by constants;  then materials and properties, solids and logical and physical volumes; finally the whole geomtery can be saved as a GDML file and/or visualised using VTK.

@@

An example of the VTK output for code Listing~\ref{lst:pythonRapidModelling} is shown in 
Figure~\ref{fig:rapidModellingExample}.
\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.9\columnwidth]{./diagrams/rapidModelling.pdf}
\caption{VTK visualisation output from code Listing~\ref{lst:pythonRapidModelling}.}
\label{fig:rapidModellingExample}
\end{center}
\end{figure}
Significantly more complex geometries can be developed using a structure similar to 
that shown in code Listing~\ref{lst:pythonRapidModelling}.

>>>>

\section{Rapid geometry modelling}
Given the Python scripting interface, expression  and tessellation engines it is possible for a user to rapidly specify the geometrical layout of the RT problem, vary 
the parameters of the geometry and visualise it.  When a user has achieved the desired geometry, without geometry overlaps, a GDML file can be written to disk from the internal memory representation. Some example code is presented in Listing~\ref{lst:pythonRapidModelling}. The structure should be familiar to regular 
users of Geant4 or GDML, apart from the new class described in the previous section called the \pyinline{Registry}. First the \verb|Registry| is created to store all the \PYGEOMETRY{} objects; followed by constants;  then materials and properties, solids and logical and physical volumes; finally the whole geomtery can be saved as a GDML file or visualised using VTK.

@@

An example of the VTK output for code
Listing~\ref{lst:pythonRapidModelling} is shown in
Figure~\ref{fig:rapidModellingExample}. Significantly more complex
geometries can be developed using a structure similar to that shown.

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.9\columnwidth]{./diagrams/rapidModelling.pdf}
\caption{VTK visualisation output from code Listing~\ref{lst:pythonRapidModelling}.}
\label{fig:rapidModellingExample}
\end{center}
\end{figure}
